Taking Dyads Seriously

### 2018-02-22 paper/4_app.tex
changes
basically adding a new writeup of gibler to the app section.

\subsection{....}

@@

mcdonald we recover support fro trade dependenicence and also find eveidence for their highest barrier to trade variable

@@

for gibler

>>>>

\subsection{Gibler}
The allied variable along with contiguity and joint-democracy comprise the so-called ``control variables'' that are required by the literature. The coefficient for the allied variable is negative and imprecisely measured (non-significant in Gibler's terminology). It has about the same size when estimated with AME, but is very precisely measured and would be adjudged as very important in Gibler's initial assessment.   The joint-democracy variable is negative and has a small standard error ($\sigma_{\hat{\beta}}$) in Gibler's Table 6, but when estimated with AME it has virtually zero magnitude and a standard error larger than this, indicating that it has no strong independent effect. Both Gibler's estimate and that derived with AME for contiguity show that it is an important independent stimulant to conflict.

Turning away from the less interesting control variables, both approaches show that, consistent with Gibler's argument, parity does not exhibit a strong, precise impact on conflict. Rivalry is positive and precisely measured as an influence on conflict with both approaches, though it is about $65\%$ smaller and an order of magnitude more precisely measured by AME. Turning to Gibler's main argument, while the logit reported by Gibler confirms his hypothesis that parity at the entry year is very important to the onset of conflicts (positive and precisely measured), this effect is competely eliminated when the dependencies in the data are taken into account by the AME estimation.

Gibler's argument that parity is unimportant because it is static is borne out in both estimations. But his argument that parity at the time at which a country enters the international system determines---in part---its propensity toward militarized dispute onsets is not borne out at all.

Finally, we might ask about the performance of Gibler's model when estimated with standard (logit) approaches, compared to its performance using the AME framework. As shown above, the AME dominates in a predictive sense. Gibler's model is slightly better than a coin-toss in terms of correctly predicting non-onsets of MIDS, and always wrong in predicting actual onsets.  The AME approach is much more credible.

\subsection{...}

@@

%mcdonald we recover support fro trade dependenicence and also find eveidence for their highest barrier to trade variable

@@
